%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Founder/Organizer} % Job title
    {Boston Drone Racing} % Organization
    {Boston, MA} % Location
    {Jan. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Organizer for weekly races and monthly hack nights.}
      \item {Secured funding for racing track. }
      \item {Created website, designed logo, established communication channels
              and manage social
              media networks. }
      \end{cvitems}
    }

  \cventry
    {Co-Founder/CEO} % Job title
    {Capsules, LLC} % Organization
    {Madison, CT} % Location
    {June 2013 - Aug. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Managed team to create a geo-location based augmented reality
              mobile app.}
      \item {Lead mobile developer responsible for overall architechure, design and implementation.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer} % Job title
    {Sikorsky Aircraft {\scriptsize\textnormal{(subcontracted through AIS Consulting
                and Sila SG)}}} % Organization
    {Shelton, CT} % Location
    {Jun. 2006 - Jan. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Lead software engineer on seven software applications supporting the
              Sikorsky CH-53K Aircraft's Integrated Support System (ISS) for
              fleet management and IVHM. }
        \item {Responsible for integration between Sikorsky CH-53K Aircraft's
                Integrated Support System (ISS) and Goodrich ground support
                software (GSS).}
        \item {Designed and implemented continuous integration environment.}
      \end{cvitems}
    }

  \cventry
    {Co-founder/Chairman} % Job title
    {CT Hackerspace} % Organization
    {Watertown, CT} % Location
    {Aug. 2010 - Aug. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Established organization through the development of bylaws,
              identity, physical and web presence.}
      \item {Ran monthly board meetings to facilitate in the growth and direction of the hackerspace.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
