
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Boston University} % Organization
    {Boston, MA} % Location
    {Jan. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
\item {Developing next generation flight control systems through the use of
machine learning including the worlds first open-source neural network powered flight control
firmware, Neuroflight.}
      \item {Conducted research in wide area of cyber security including static
and dynamic malware analysis, vulnerability analysis, cyber defense and attacks
and mobile security.}
      \end{cvitems}
    }

  \cventry
    {Cyber Security Research Intern } % Job title
    {MIT Lincoln Laboratory} % Organization
    {Lexington, MA} % Location
    {Jan. 2016 - June 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed novel SDN attack called Persona Hijacking which has been published in USENIX Security Symposium.}
      \end{cvitems}
    }

  \cventry
    {Research Assistant} % Job title
    {Stevens Institute of Technology} % Organization
    {Hoboken, NJ} % Location
    {Jan. 2012 - Dec. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Worked on multi-discipline team consisting of biomedical and computer
engineers to advance nerve guidance conduit performance.}
       \item {Developed novel machine learning algorithms to predict nerve guidance conduit performance. }
      \end{cvitems}
    }

\end{cventries}
